---
title: "index"
output: html_document
---

```{r, echo=FALSE, message=FALSE}
library(knitr)
library(plotly)
library(dplyr)

#sets working directory
#setwd("C:/Users/justinlee/Documents/assignment-7")

# calls the data and functions
data <- read.csv("https://raw.githubusercontent.com/INFO-498F/a7-survey-data/master/intro_survey_data.csv")
source("scripts/summary.R")
source("scripts/chart_1.R")
source("scripts/Chart_2.R")

list_information <- summary_information(data)

```
#### Summary
There are `r list_information$Applying[1]` freshman, `r list_information$Applying[2]` sophmore, `r list_information$Applying[3]` juniors, `r list_information$Applying[4]` seniors that are applying for the informatics major that are currently in Info 498F.

There are `r list_information$Not_Applying[1]` freshman, `r list_information$Not_Applying[2]` sophmore, `r list_information$Not_Applying[3]` juniors, `r list_information$Not_Applying[4]` seniors that are not applying for the informatics major that are currently in Info 498F.

There are `r list_information$Mac_Users[1]` freshman, `r list_information$Mac_Users[2]` sophmore, `r list_information$Mac_Users[3]` juniors, `r list_information$Mac_Users[4]` seniors that use Macs that are currently in Info 498F with a total of `r sum(list_information$Mac_Users)` users.
However, there are a total of `r sum(list_information$Windows_Users)` Window users and `r sum(list_information$Windows_Users)` > `r sum(list_information$Mac_Users)` therefore Windows are better than Macs.


#### Chart 1
```{r, echo=FALSE}
chartOne(data)

```

####Chart 2
```{r, echo=FALSE}
chartTwo(data)

```

